\begin{thebibliography}{9}
	\bibitem{kmpp}
	M. S. Islam and C. Liu, "Know Your Customer: Computing K-Most Promising Products," \textit{The VLDB Journal}, pp. 545–570, 2016.
	
	\bibitem{dynamic-skyline}
	D. Papadias, Y. Tao, G. Fu and B. Seeger, "Progressive Skyline Computation in Database Systems," \textit{ACM Transactions on Database Systems}, Vol. 30, No. 1, pp. 41–82, 2005.
	
	\bibitem{reverse-skyline}
	E. Dellis and B. Seeger, "Efficient Computation of Reverse Skyline Queries," \textit{VLDB Endowment}, pp. 291-302, 2007.
	
	\bibitem{time-series}
	B. Jiang and J. Pei, "Online Interval Skyline Queries on Time Series," \textit{IEEE International Conference on Data Engineering}, pp. 1036-1047, 2009.
	
	\bibitem{multidimensional-database}
	M. Golfarelli and S. Rizzi, "Introduction to Data Warehousing," in \textit{Data Warehouse Design: Modern Principles and Methodologies}, New York: McGraw-Hill, 2009, pp. 1-42. 
	
	\bibitem{skyline}
	S. Borzsonyi, D. Kossmann and K. Stocker, "The Skyline Operator," \textit{In: ICDE}, pp. 421-430, 2001.
	
	\bibitem{dynamic-skyline-2}
	L. Zou, L. Chen, M. T. Özsu and D. Zhao, "Dynamic Skyline Queries in Large Graphs," \textit{DASFAA'10 Proceedings of the 15th International Conference on Database Systems for Advanced Applications - Volume Part II}, pp. 62-78, 2010.
	
	\bibitem{mid-skyline}
	X. Wu, Y. Tao, R. C.-W. Wong, L. Ding and J. X. Yu, "Finding the Influence Set through Skylines," \textit{EDBT}, pp. 1030-1041, 2009.
	
	\bibitem{paralel}
	G.S. Almasi and A. Gottlieb, \textit{Highly Parallel Computing}. Redwood City, CA: Benjamin-Cummings Publishers, 1989.
	
	\bibitem{data}
	Merriam-webster.com. "Definition of DATA". [Online]. Available: https://www.merriam-webster.com/dictionary/data. [Accessed 13 Mei 2019]
	
	\bibitem{python}
	Python.org. “What is Python? Executive Summary”. [Online]. Available: https://www.python.org/doc/essays/blurb/. [Accessed 18 Mei 2019].
	
	\bibitem{flask}
	Flask.pocoo.org. "Welcome to Flask". [Online]. Available: http://flask.pocoo.org/docs/1.0/. [Accessed 18 Mei 2019]
	
	\bibitem{visjs}
	Visjs.org. "Vis.js". [Online]. Available: https://visjs.org/. [Accessed 9 Juni 2019]
	
	\bibitem{fc}
	J. A. Blackard, D. J. Jean and C. W. Anderson, "UCI
	Machine Learning Repositories," 1 Agustus 1998. [Online].
	Available: https://archive.ics.uci.edu/ml/datasets/covertype.
	[Accessed 9 Juni 2018].
		
\end{thebibliography}
